paper3

### 2022-07-08 paper3.Rmd
AUC

    model = xgb.XGBClassifier(params,
                              eval_metric = "rmse", 
                              n_estimators = 2000)

    model.fit(X_train, y_train)

@@

>>>>

    model = xgb.XGBClassifier(params,
                             # eval_metric = "rmse", 
                              n_estimators = 2000)

    model.fit(X_train, y_train,
              eval_metric = 'auc')

@@

```{python}
def objective(space):
    clf=xgb.XGBClassifier(n_estimators =space['n_estimators'], 
                          max_depth = int(space['max_depth']), 
                          gamma = space['gamma'],
                          reg_alpha =  int(space['reg_alpha']),
                          min_child_weight=int(space['min_child_weight']),
                          colsample_bytree=int(space['colsample_bytree']))

    evaluation = [( X_train, y_train), ( X_test, y_test)]

    clf.fit(X_train, y_train,
            eval_set=evaluation, eval_metric="auc",
            early_stopping_rounds=10,verbose=False)

    pred = clf.predict(X_test)
    accuracy = accuracy_score(y_test, pred>0.5)
    print ("SCORE:", accuracy)
    return {'loss': -accuracy, 'status': STATUS_OK }
